---
title: "gfAnalysis"
author: "Colin T. Annand"
date: "4/5/2020"
output: html_document
---

```{r setup, include=FALSE}
# knitr::opts_chunk$set(echo = TRUE)
load("All_Subjs.Rdata")
```
Code chunk below was used to name and create All_Subs.Rdata.
```{r}
Subs_name_list <- list.files(path = "~/Documents/GitHub/GripForce_Recognition", full.names = T,recursive = TRUE, pattern = ".csv" )

library(data.table)
Sub_List <- lapply(Subs_name_list,fread)
names(Sub_List) <- gsub(x = Subs_name_list, pattern = "/Users/cannand/Documents/GitHub/GripForce_Recognition/SubjDATA/P1/", replacement = "")
```
Some basic plotting ideas (Grip force changes and response time)
```{r}
#ex
trial_ex <- Sub_List[[1]]
head(trial_ex,2)
# plot
plot(trial_ex$tx,trial_ex$rs_left, type = "l", col = "blue") +
points(trial_ex$tx,trial_ex$rs_right,type = "l", col = "red") +

#extract RT from fname and plot as line
name <- names(Sub_List[1])
t1_info <- strsplit(name,split = "_")
RT <- (as.numeric(t1_info[[1]][8]))/1000
abline(h=0,v=RT, col = "green")

```

```{r}
getalign <- function(df){
  name <- deparse(substitute(df))
  cond_info <- strsplit(name, split="_")  
  if (cond_info[11] == "L.jpg") {
    Aligned_SD <- var(df$rs_left)
    UnalignedSD <- var(df$rs_right)
  } else {
    Aligned_SD <- var(df$rs_right)
    UnalignedSD <- var(df$rs_left)
  }
  return(c(Aligned_SD,UnalignedSD))
}

load("All_Subjs.Rdata") 
blank_array <- array(data = 0,dim = c(6840,2)) #make array of the list size, with 2 columns for align/unalign

for (i in 1:length(Sub_List)){  #fill the array using getalign() function
  temp_result <- getalign(Sub_List[[i]])
  blank_array[i,1] <- temp_result[1]
  blank_array[i,2] <- temp_result[2]
}
nn <- names(Sub_List) #names from Sub list
nn <- gsub(nn,pattern = "/Users/cannand/Documents/GitHub/GripForce_Recognition/SubjDATA/",replacement = "")

tt_align <- data.frame(nn,blank_array[,1],blank_array[,2]) #new_dataframe(can be exported if needed)
names(tt_align) <- c("Subj&Trial","AlignedVAR","UnalignedVAR") #name the dataframe
save(tt_align,file = "tt_align.Rdata")

#load("tt_align.Rdata")
t.test(tt_align$AlignedVAR,tt_align$UnalignedVAR)

library("tidyr") 
ALL_t.test <- separate(data = tt_align, col = "Subj&Trial", into = c("Subj","1","Block","1","Trial","1","RT","5307","BA1","grizzly","L.jpg","Lvalue.txt.csv"),sep = "_", remove = T, fill = "right")

Final_Set <- subset(ALL_t.test,select = c("1","1","1","5307","BA1","grizzly","L.jpg","AlignedVAR","UnalignedVAR"))
names(Final_Set) <- c("Subj","Block","Trial","RT","Cond","stimuli","direction","AlignedVAR","UnalignedVAR")


Final_Set$Cond <- gsub(Final_Set$Cond,pattern = "[[:digit:]]",replacement = "")

Final_Set$Cond <- gsub(Final_Set$Cond,pattern = "A",replacement = "Animal")
Final_Set$Cond <- gsub(Final_Set$Cond,pattern = "T",replacement = "Tool")
Final_Set$direction <- gsub(Final_Set$direction,pattern = "L.jpg",replacement = "Left")
Final_Set$direction <- gsub(Final_Set$direction,pattern = "R.jpg",replacement = "Right")

head(Final_Set)
write.csv(Final_Set,"GF_Variance_by_Hand_ALL_Subs.csv",row.names = F)
```

########## This is the output format we want (creating above)
OUTPUT FORMAT
Subj  / TrialN  / Block / Stim  / Unaligned / Aligned / RT  
1       2         1       grizzly       345       123     800

```{r}
P1 <- unlist(strsplit(names(Sub_List[1]),split = "_"))
P1

ALL_DATA <- data.frame(P1[2],P1[4],P1[6],P1[8],tt_align$AlignedVAR,tt_align[1]$UnalignedVAR)
names(ALL_DATA) <- c(P1[1],P1[3],P1[5],P1[7])


ALL_DATA

```

cond_info <- strsplit(name, split="_")  


For every trial, compare aligned variance to unaligned variance : Ignore participant, Ignore Block, Ignoring Condition.

